---
title: "citybikes-introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{citybikes-introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(citybikes)
```

# Introduction

`citybikesR` is an R package that connects to the CityBikes API
to retrieve information about bike-sharing networks and their stations.

The package allows users to search for bike-sharing networks by city
or country and retrieve information about the stations in a selected
network, including the number of currently available bikes.

## Finding bike-sharing networks

The `find_networks()` function can be used to search for
bike-sharing networks by city or country.

For example, we can search for networks in Göteborg:

```{r}
find_networks(city = "Göteborg")
```
## Getting station information

Once we have identified a bike-sharing network, we can use
`get_stations()` to retrieve information about its stations.

For example, we can retrieve the stations for a selected network:

```{r}
stations <- get_stations("e-cargobike-goteborg")
stations
```

The returned data contains information such as the station name,
location, number of available bikes, and number of available spaces.

## Summary

The `citybikesR` package provides a simple way to access
bike-sharing information through the CityBikes API.

The main functions allow users to find bike-sharing networks
and retrieve current information about their stations.
